\documentclass[16pt]{article}

\usepackage[utf8]{inputenc}

\usepackage{hyperref}

\usepackage[margin=0.5in]{geometry}

\title{Team Venom Coders MAD 5272 Project Presentation Document}

\author{Venom Coders}

\date{ 08/11/2020}




\begin{Project document}




\maketitle




\section * {Venom Coders Members}

\begin{enumerate}

\item Lijosh Abraham C0764921 

\item Noel Abraham Reji C0765766
\item Vibin Erapakkal Joby C0765779 
\item Yadhukrishnan Ekambaran C0765769

\end{enumerate}




\section * {The Vision and Concept our Project}




Punch Me Application 
We Venom Coders intends to produce an IOS and android Application for effective time and work management for employees.The Application will deliver the functionalities of Clock In and Out of shifts accordingly, view the logs of worked and get an overall picture and a abstract report, Scheduling and planing the shifts ahead and gets notified respectively, Custom user interfaces and adding multiple jobs and editing them upon user needs.




Our Vision is that this product will be of value to customers who are employees who work in hourly basis. They will be provided with an effective way to manage their schedule and optimized records of their shifts.




\section * {Work Breakdown Structure}
The Work is been divided between our members making maximizing their strengths.
Lijosh Abraham will be doing the designing the application according to the market trends and developing the onboarding screen for the application.
Noel Abraham Reji will be doing the documentation of the project including the market research , testing the whole application and there by developing the settings screens.
Vibin Erapakkal Joby will be doing the developing of the scheduling, home and the login screens with the server hosting.
Yadhukrishnan Ekambaran will be doing  the development of the log screens and the optimized back end apis.

The work is evenly distributed for the Punch Me version 1.0 which is the MVP for  24th August 2020.

\subsection   {Critical Path}
Our project will be following agile methodology where the Members are divided and provided small tasks.Each Sprint will be of 1 week and our project deliverables to be presented very weeks in sprint in the team. Week 1 will be having the design and market analysis with test case preparation and the developing the back end of our application.Week 2 will be developing the application and server hosting with adequate data sets.With a 3 week project the Week 2 deliverable is critical since it is the planned date for a stable build and start testing. Week 3 is for the Testing and Bug fixing.

\section * {GANTT Chart}




\begin{enumerate}

    \item 7 August 2020 to 12 August 2020 - Week 1
Tasks: Designing , Test Case Preparation, Back end api creation

    \item 13 August 2020 to 18 August 2020 - Week 2
Tasks: Developing the Screens and server services

    





    \item 19 August 2020 to 24 August 2020 - Week 3
Tasks: Testing and bug fixes with the deployment into production server

\end{enumerate}

  

\section{Assignment: Punch Me by Venom Coders}  

\subsection{The handin work is to be presented in Latex, submitted to GitHub}







\end{document}
